Inefficient Concessions and Mediation

### 2021-02-23 draft.tex
add back in author information and acknowledgements

\title{Inefficient Concessions and Mediation}
%\author{Kristy Buzard\\ \footnote{We thank Eli Berman, Renee Bowen, Ben Graham, Joel Watson as well as seminar
%participants at ... for helpful discussions and comments. Affan Rahman and Apurvi Bhartia provided excellent research assistance.}
%Syracuse University \\
%kbuzard@syr.edu\\
%\\
%Ben Horne\\ 
%University of California, San Diego\\
%\\}
\date{\today}

>>>>

\title{Inefficient Concessions and Mediation}
\author{Kristy Buzard\footnote{We thank Eli Berman, Renee Bowen, Ben Graham, and Joel Watson as well as generous seminar
participants for helpful discussions and comments. Affan Rahman and Apurvi Bhartia provided excellent research assistance. All remaining errors are our own.}\\
Syracuse University \\
kbuzard@syr.edu\\
\\
Ben Horne\\ 
University of California, San Diego\\
\\}
\date{\today}
